taxadb: A High-Performance Local Taxonomic Database Interface

### 2019-01-02 paper/manuscript.Rmd

```{r}
url <- "ftp://ftpext.usgs.gov/pub/er/md/laurel/BBS/DataFiles/SpeciesList.txt"
col_names <- c("Seq", "AOU", "English_Common_Name", "French_Common_Name",
               "Spanish_Common_Name", "ORDER", "Family", "Genus", "Species")
bbs <- readr::read_table("bbs.txt", 
                         skip = 9, 
                         col_names = col_names, 
                         col_types = "ccccccccc")

>>>>

```{r}
url <- "ftp://ftpext.usgs.gov/pub/er/md/laurel/BBS/DataFiles/SpeciesList.txt"
col_names <- c("Seq", "AOU", "English_Common_Name", "French_Common_Name",
               "Spanish_Common_Name", "ORDER", "Family", "Genus", "Species")
bbs <- readr::read_table(url, 
                         skip = 9, 
                         col_names = col_names, 
                         col_types = "ccccccccc")
